---
title: "Beer_Brew_ analysis"
author: "Steven Hayden, Thejas Prasad"
date: "October 10, 2017"
output: 
  html_document:
    keep_md: true
---

install.packages("sqldf")
library("sqldf")
```{r echo=TRUE}
#install.packages("data.table")
#library("data.table")
```

Report the number of NA's in each column.
```{r echo=TRUE}
#3

colSums(is.na(beer_brew_merge))

```


Compute the median alcohol content and international bitterness unit for each state. 
```{r echo=TRUE}


# 4. 
#Uses SQL to group data by state (like the tapply functtion) and provied the Median ABV and Median IBU
ABV_IBU_Median = (sqldf("SELECT median(ABV) as ABV_Median,median(IBU) as IBU_Median, State FROM beer_brew_merge GROUP By State"))



```


 
Which state has the maximum alcoholic (ABV) beer? 
```{r echo=TRUE}
# 5. 
#Finds the max ABV and the state Associated with it
beer_brew_merge[which(beer_brew_merge$ABV==max(beer_brew_merge$ABV,na.rm = TRUE)),"State"]

```


Which state has the most bitter (IBU) beer?
```{r echo=TRUE}
#Alternitive methode

bbm = data.table(beer_brew_merge)

max_ibu = max(bbm[, IBU], na.rm = TRUE)

bbm[IBU == max_ibu, .(State, IBU)]
```




Summary statistics for the ABV variable
```{r echo=TRUE}
# 6. Summary statistics for the ABV variable
summary(beer_brew_merge$ABV, na.rm = TRUE)
```

Relationship between bitterness and alcohol

```{r echo=TRUE}

# 7. Is there an apparent relationship between the bitterness of the beer and its alcoholic
# content? Draw a scatter plot.
# You are welcome to use the ggplot2 library for graphs. Please ignore missing values in
# your analysis. Make your best judgment of a relationship and EXPLAIN your answer.



#import data


# Data Frame -> Low = 1, Low-Medium = 2, Medium-High = 3, High = 4

df1 = data.frame(beer_brew_merge, na.rm = TRUE)


#Linear reg

regressor = lm(formula = IBU ~ ABV, data=df1 )


#predict
y_pred = predict(regressor, newdata = df1 )



